%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Preston Crowe} & Email : \href{mailto:prestonjcrowe@gmail.com.com}{prestonjcrowe@gmail.com}\\
  \href{http://prestoncrowe.com}{www.prestoncrowe.com} & Mobile : (415) 265 - 3937 \\
  &\href{http://www.github.com/prestonjcrowe}{Github: prestonjcrowe}\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Washington}{Seattle, WA}
      {Computer Science [Dean's List, 3.71 GPA]}{Sep. 2016 -- June. 2020} \vspace{5pt}\\
      \textbf{\small Relevant Coursework:} \small Security, Cryptography, Networks, Hardware/Software Interface, Data Management, OS, AI
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Baffin Bay Networks}{Seattle, WA}
      {Software Intern}{June 2019 - September 2019}
      \resumeItemListStart
        \resumeItem{Data Collection and Full Stack Development}
        {Worked on the data collection and analysis team to provide valuable insights from the traffic collected by a sophisticated sensor network. Contributed to a multitude of projects ranging from customizing logging solutions in open source services, improving custom proprietary data collection services, and developing the API and initial mockup for Baffin Bay's Threat Insight platform. Prototyped an internal data dashboard for monitoring the state, location, and cost of the sensor network.}
      \resumeItemListEnd

    \resumeSubheading
      {F5 Networks}{Seattle, WA}
      {Software Intern}{June 2018 - September 2018}
      \resumeItemListStart
        \resumeItem{F5 Labs}
        {I worked with a team of security researchers at F5 Labs to develop a serverless vulnerability data pipeline and API. I visualized attack data including a live threat map and contributions to \href{https://www.f5.com/labs/articles/threat-intelligence/breaking-down-the-door-to-emergency-services-through-cellular-io}{Black Hat talk}. I processed CVE data (frequency, severity, etc.) and devised metrics to contribute my colleague's research.}
      \resumeItemListEnd
    
    \resumeSubheading
      {University of Washington}{Seattle, WA}
      {Teaching Assistant}{April 2018 - June 2018}
      \resumeItemListStart
        \resumeItem{Computer Programming II TA}
        { Taught two sections a week. Attended staff meetings, contributed to section planning, and graded assignments. Wrote and shared with my students a suite of example applications to dive deeper into the lecture material, including a brute force password guesser and a recersive puzzle solver.}
      \resumeItemListEnd


    \resumeSubheading
      {NASA AMES Research Center}{Mountain View, CA}
      {Software Intern}{June 2017 - September 2017}
      \resumeItemListStart
        \resumeItem{OpenMCT}
        {OpenMCT is an open source mission control framework developed in AngularJS. I implemented JSON import and export functionality for workspaces and folder hierarchies, allowing for standardization of layouts across teams. The software is still being tested extensively at JPL and with the addition of modular workspaces, the process of creating and sharing demo environments has been expedited. Worked on a large team in an enterprise environment; wrote extensive tests for each piece of code I contributed.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}

  \resumeSubHeadingListStart
  \resumeSubItem{\href{https://github.com/prestonjcrowe/shop-goodwill-bot}{Goodwill Bot}}
    {Watches shopgoodwill.com (auction site) and sends me an email when an interesting item is about to sell for a low price. Easily configurable.}
  \resumeSubItem{\href{https://riemann-sums.github.io}{Riemann Sum Visualization}}
      {Web applet that allows students to plot a curve and compute a variety of Riemann Sum values with custom function, bounds, and interval size. Built as a tool for my high school calculus teacher to use in his classroom as well as a method of checking my own answers on assignments. It is freely available online for curious students to experiment with.}
      \resumeSubItem{\href{https://www.github.com/prestonjcrowe/mtg-lifecounter}{MTG Life Counter App}}
      {Android application that keeps track of one or two player's life totals during a game of Magic: The Gathering. The application supports both EDH and standard formats. The source code is freely available on my Github page.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \item{
            \textbf{Proficient:} {Golang, Javascript, React, Python, Java, Android SDK, Git, d3, C, GNU/Linux, MongoDB, Postgresql, Node}
    }
    \item {
            \textbf{Some Experience:} {Angular, AWS (Lambda, S3, Gateway, ElasticSearch, Route53, EC2), Ruby / Ruby on Rails, Racket, C++, SML, Nginx, Mininet, SQLite}
    }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
